Evolution of the AGN UV luminosity function from redshift 7.5

### 2018-07-25 Paper/paper.tex

\author[Kulkarni et al.]
       {{Girish Kulkarni$^{1,2}$\thanks{Email: kulkarni@ast.cam.ac.uk},
           G\'abor Worseck$^{3,5}$
           and Joseph F.~Hennawi$^{4,5}$} \\
         $^1$Institute of Astronomy,
         University of Cambridge, Madingley Road, Cambridge CB3 0HA,
         UK \\
         $^2$Kavli Institute of Cosmology,
         University of Cambridge, Madingley Road, Cambridge CB3 0HA,
         UK \\
         $^2$Institut f\"ur Physik und Astronomie, Universit\"at
         Potsdam, Karl-Liebknecht-Stra\ss e\ 24/25, D-14476 Potsdam,
         Germany \\
         $^4$Department of Physics, Broida Hall, UC Santa Barbara,
         Santa Barbara, CA 93106-9530, USA\\
         $^5$Max Planck Institute for Astronomy, K\"onigstuhl 17,
         D-69117 Heidelberg, Germany}
       \date{Accepted ---. Received ---; in original form ---}

@@

    &
    &
    &
    &
    &
    \multicolumn{1}{c}{cMpc$^{-3}$mag$^{-1}$)} &
    &
    & \\
    \hline
    0.31$^a$ & 0.10 & 0.40 & 3520 & 3632 & -5.62^{+0.09}_{-0.11} & -21.37^{+0.21}_{-0.23} & -2.94^{+0.09}_{-0.10} & -1.22^{+0.18}_{-0.16} \\
    0.50$^a$ & 0.40 & 0.60 & 4555 & 4686 & -6.13^{+0.04}_{-0.04} & -23.00^{+0.08}_{-0.07} & -3.38^{+0.08}_{-0.08} & -1.36^{+0.04}_{-0.04} \\
    0.72 & 0.60 & 0.80 & 3308 & 4684 & -6.42^{+0.09}_{-0.08} & -24.03^{+0.14}_{-0.13} & -3.56^{+0.12}_{-0.13} & -1.75^{+0.04}_{-0.04} \\
    0.91 & 0.80 & 1.00 & 3922 & 5248 & -6.39^{+0.08}_{-0.08} & -24.50^{+0.12}_{-0.12} & -3.69^{+0.11}_{-0.11} & -1.73^{+0.06}_{-0.05} \\
    1.10 & 1.00 & 1.20 & 6367 & 6566 & -6.54^{+0.03}_{-0.03} & -25.15^{+0.04}_{-0.04} & -4.18^{+0.08}_{-0.08} & -1.73^{+0.02}_{-0.02} \\
    1.30 & 1.20 & 1.40 & 6479 & 7132 & -6.42^{+0.04}_{-0.04} & -25.29^{+0.06}_{-0.05} & -3.97^{+0.08}_{-0.08} & -1.74^{+0.03}_{-0.03} \\
    1.50 & 1.40 & 1.60 & 7539 & 7771 & -6.51^{+0.03}_{-0.03} & -25.67^{+0.04}_{-0.04} & -4.28^{+0.08}_{-0.08} & -1.76^{+0.02}_{-0.02} \\
    1.71 & 1.60 & 1.80 & 6788 & 7421 & -6.29^{+0.03}_{-0.03} & -25.56^{+0.05}_{-0.05} & -3.96^{+0.07}_{-0.07} & -1.60^{+0.03}_{-0.03} \\
    1.98 & 1.80 & 2.20 & 10478 & 10876 & -6.72^{+0.03}_{-0.03} & -26.26^{+0.04}_{-0.04} & -4.21^{+0.07}_{-0.07} & -1.87^{+0.02}_{-0.02} \\
    2.30$^a$ & 2.20 & 2.40 & 8419 & 8419 & -6.16^{+0.07}_{-0.06} & -25.49^{+0.12}_{-0.11} & -3.34^{+0.12}_{-0.12} & -1.61^{+0.04}_{-0.04} \\
    2.45$^a$ & 2.40 & 2.50 & 3403 & 3403 & -6.40^{+0.08}_{-0.07} & -25.86^{+0.14}_{-0.12} & -3.61^{+0.21}_{-0.22} & -1.60^{+0.05}_{-0.04} \\
    2.55$^a$ & 2.50 & 2.60 & 2640 & 2640 & -6.15^{+0.08}_{-0.08} & -25.34^{+0.17}_{-0.16} & -3.32^{+0.15}_{-0.16} & -1.39^{+0.08}_{-0.07} \\
    2.65$^a$ & 2.60 & 2.70 & 1883 & 1883 & -5.98^{+0.05}_{-0.06} & -25.15^{+0.13}_{-0.14} & -3.12^{+0.12}_{-0.12} & -1.05^{+0.09}_{-0.08} \\
    2.75$^a$ & 2.70 & 2.80 & 1135 & 1135 & -6.29^{+0.08}_{-0.07} & -25.94^{+0.15}_{-0.13} & -3.78^{+0.27}_{-0.30} & -1.34^{+0.07}_{-0.06} \\
    2.85$^a$ & 2.80 & 2.90 & 1069 & 1069 & -6.45^{+0.11}_{-0.10} & -26.22^{+0.21}_{-0.18} & -3.61^{+0.35}_{-0.41} & -1.46^{+0.08}_{-0.07} \\
    2.95$^a$ & 2.90 & 3.00 & 1104 & 1104 & -6.76^{+0.07}_{-0.06} & -26.53^{+0.11}_{-0.09} & -5.05^{+0.59}_{-0.63} & -1.71^{+0.05}_{-0.04} \\
    3.05$^a$ & 3.00 & 3.10 & 1127 & 1127 & -6.77^{+0.08}_{-0.07} & -26.48^{+0.12}_{-0.11} & -4.68^{+0.44}_{-0.52} & -1.70^{+0.06}_{-0.05} \\
    3.15$^a$ & 3.10 & 3.20 & 1041 & 1041 & -7.26^{+0.16}_{-0.11} & -27.11^{+0.22}_{-0.17} & -4.38^{+0.76}_{-1.30} & -1.96^{+0.07}_{-0.05} \\
    3.25$^a$ & 3.20 & 3.30 & 815 & 815 & -7.34^{+0.13}_{-0.13} & -27.20^{+0.20}_{-0.22} & -4.39^{+0.69}_{-0.79} & -1.94^{+0.06}_{-0.05} \\
    3.34$^a$ & 3.30 & 3.40 & 510 & 510 & -7.54^{+0.21}_{-0.21} & -27.39^{+0.28}_{-0.37} & -4.67^{+1.38}_{-1.44} & -2.08^{+0.09}_{-0.07} \\
    3.44$^a$ & 3.40 & 3.50 & 155 & 155 & -6.76^{+0.19}_{-0.20} & -26.62^{+0.40}_{-0.36} & -3.67^{+0.62}_{-0.83} & -1.24^{+0.28}_{-0.23} \\
    3.88 & 3.70 & 4.10 & 628 & 1204 & -7.91^{+0.11}_{-0.11} & -27.26^{+0.13}_{-0.12} & -4.83^{+0.33}_{-0.38} & -2.07^{+0.10}_{-0.09} \\
    4.35 & 4.10 & 4.70 & 442 & 603 & -8.32^{+0.29}_{-0.25} & -27.37^{+0.37}_{-0.30} & -4.20^{+0.41}_{-0.50} & -2.21^{+0.15}_{-0.13} \\
    4.92 & 4.70 & 5.50 & 263 & 263 & -9.02^{+0.30}_{-0.21} & -27.89^{+0.37}_{-0.26} & -4.58^{+0.71}_{-0.80} & -2.30^{+0.11}_{-0.08} \\
    6.00 & 5.50 & 6.50 & 66 & 66 & -10.66^{+0.74}_{-1.11} & -29.21^{+1.08}_{-1.89} & -5.05^{+0.76}_{-1.18} & -2.41^{+0.10}_{-0.08} \\
    \hline
  \end{tabular}\\
  \begin{minipage}{13.0cm}
    \textsuperscript{$a$}{Redshift bin not considered in the joint QLF fit due to systematic errors (open circles in Figure~\ref{fig:mosaic}).}
  \end{minipage}
\end{table*}

>>>>

\author[Kulkarni et al.]
       {{Girish Kulkarni$^{1,2}$\thanks{Email: kulkarni@ast.cam.ac.uk},
           G\'abor Worseck$^{3,5}$
           and Joseph F.~Hennawi$^{4,5}$} \\
         $^1$Institute of Astronomy,
         University of Cambridge, Madingley Road, Cambridge CB3 0HA,
         UK \\
         $^2$Kavli Institute of Cosmology,
         University of Cambridge, Madingley Road, Cambridge CB3 0HA,
         UK \\
         $^3$Institut f\"ur Physik und Astronomie, Universit\"at
         Potsdam, Karl-Liebknecht-Stra\ss e\ 24/25, D-14476 Potsdam,
         Germany \\
         $^4$Department of Physics, Broida Hall, UC Santa Barbara,
         Santa Barbara, CA 93106-9530, USA\\
         $^5$Max Planck Institute for Astronomy, K\"onigstuhl 17,
         D-69117 Heidelberg, Germany}
       \date{Accepted ---. Received ---; in original form ---}

@@

    &
    &
    &
    &
    &
    \multicolumn{1}{c}{cMpc$^{-3}$mag$^{-1}$)} &
    &
    & \\
    \hline
    0.31$^a$ & 0.10 & 0.40 & 3520 & 3632 & -5.62^{+0.09}_{-0.11} & -21.37^{+0.21}_{-0.23} & -2.94^{+0.09}_{-0.10} & -1.22^{+0.18}_{-0.16} \\
    0.50$^a$ & 0.40 & 0.60 & 4555 & 4686 & -6.13^{+0.04}_{-0.04} & -23.00^{+0.08}_{-0.07} & -3.38^{+0.08}_{-0.08} & -1.36^{+0.04}_{-0.04} \\
    0.72 & 0.60 & 0.80 & 3308 & 4684 & -6.42^{+0.09}_{-0.08} & -24.03^{+0.14}_{-0.13} & -3.56^{+0.12}_{-0.13} & -1.75^{+0.04}_{-0.04} \\
    0.91 & 0.80 & 1.00 & 3922 & 5248 & -6.39^{+0.08}_{-0.08} & -24.50^{+0.12}_{-0.12} & -3.69^{+0.11}_{-0.11} & -1.73^{+0.06}_{-0.05} \\
    1.10 & 1.00 & 1.20 & 6367 & 6566 & -6.54^{+0.03}_{-0.03} & -25.15^{+0.04}_{-0.04} & -4.18^{+0.08}_{-0.08} & -1.73^{+0.02}_{-0.02} \\
    1.30 & 1.20 & 1.40 & 6479 & 7132 & -6.42^{+0.04}_{-0.04} & -25.29^{+0.06}_{-0.05} & -3.97^{+0.08}_{-0.08} & -1.74^{+0.03}_{-0.03} \\
    1.50 & 1.40 & 1.60 & 7539 & 7771 & -6.51^{+0.03}_{-0.03} & -25.67^{+0.04}_{-0.04} & -4.28^{+0.08}_{-0.08} & -1.76^{+0.02}_{-0.02} \\
    1.71 & 1.60 & 1.80 & 6788 & 7421 & -6.29^{+0.03}_{-0.03} & -25.56^{+0.05}_{-0.05} & -3.96^{+0.07}_{-0.07} & -1.60^{+0.03}_{-0.03} \\
    1.98 & 1.80 & 2.20 & 10478 & 10876 & -6.72^{+0.03}_{-0.03} & -26.26^{+0.04}_{-0.04} & -4.21^{+0.07}_{-0.07} & -1.87^{+0.02}_{-0.02} \\
    2.30$^a$ & 2.20 & 2.40 & 8419 & 8419 & -6.16^{+0.07}_{-0.06} & -25.49^{+0.12}_{-0.11} & -3.34^{+0.12}_{-0.12} & -1.61^{+0.04}_{-0.04} \\
    2.45$^a$ & 2.40 & 2.50 & 3403 & 3403 & -6.40^{+0.08}_{-0.07} & -25.86^{+0.14}_{-0.12} & -3.61^{+0.21}_{-0.22} & -1.60^{+0.05}_{-0.04} \\
    2.55$^a$ & 2.50 & 2.60 & 2640 & 2640 & -6.15^{+0.08}_{-0.08} & -25.34^{+0.17}_{-0.16} & -3.32^{+0.15}_{-0.16} & -1.39^{+0.08}_{-0.07} \\
    2.65$^a$ & 2.60 & 2.70 & 1883 & 1883 & -5.98^{+0.05}_{-0.06} & -25.15^{+0.13}_{-0.14} & -3.12^{+0.12}_{-0.12} & -1.05^{+0.09}_{-0.08} \\
    2.75$^a$ & 2.70 & 2.80 & 1135 & 1135 & -6.29^{+0.08}_{-0.07} & -25.94^{+0.15}_{-0.13} & -3.78^{+0.27}_{-0.30} & -1.34^{+0.07}_{-0.06} \\
    2.85$^a$ & 2.80 & 2.90 & 1069 & 1069 & -6.45^{+0.11}_{-0.10} & -26.22^{+0.21}_{-0.18} & -3.61^{+0.35}_{-0.41} & -1.46^{+0.08}_{-0.07} \\
    2.95$^a$ & 2.90 & 3.00 & 1104 & 1104 & -6.76^{+0.07}_{-0.06} & -26.53^{+0.11}_{-0.09} & -5.05^{+0.59}_{-0.63} & -1.71^{+0.05}_{-0.04} \\
    3.05$^a$ & 3.00 & 3.10 & 1127 & 1127 & -6.77^{+0.08}_{-0.07} & -26.48^{+0.12}_{-0.11} & -4.68^{+0.44}_{-0.52} & -1.70^{+0.06}_{-0.05} \\
    3.15$^a$ & 3.10 & 3.20 & 1041 & 1041 & -7.26^{+0.16}_{-0.11} & -27.11^{+0.22}_{-0.17} & -4.38^{+0.76}_{-1.30} & -1.96^{+0.07}_{-0.05} \\
    3.25$^a$ & 3.20 & 3.30 & 815 & 815 & -7.34^{+0.13}_{-0.13} & -27.20^{+0.20}_{-0.22} & -4.39^{+0.69}_{-0.79} & -1.94^{+0.06}_{-0.05} \\
    3.34$^a$ & 3.30 & 3.40 & 510 & 510 & -7.54^{+0.21}_{-0.21} & -27.39^{+0.28}_{-0.37} & -4.67^{+1.38}_{-1.44} & -2.08^{+0.09}_{-0.07} \\
    3.44$^a$ & 3.40 & 3.50 & 155 & 155 & -6.76^{+0.19}_{-0.20} & -26.62^{+0.40}_{-0.36} & -3.67^{+0.62}_{-0.83} & -1.24^{+0.28}_{-0.23} \\
    3.88 & 3.70 & 4.10 & 628 & 1204 & -7.91^{+0.11}_{-0.11} & -27.26^{+0.13}_{-0.12} & -4.83^{+0.33}_{-0.38} & -2.07^{+0.10}_{-0.09} \\
    4.35 & 4.10 & 4.70 & 442 & 603 & -8.32^{+0.29}_{-0.25} & -27.37^{+0.37}_{-0.30} & -4.20^{+0.41}_{-0.50} & -2.21^{+0.15}_{-0.13} \\
    4.92 & 4.70 & 5.50 & 263 & 263 & -9.02^{+0.30}_{-0.21} & -27.89^{+0.37}_{-0.26} & -4.58^{+0.71}_{-0.80} & -2.30^{+0.11}_{-0.08} \\
    6.00 & 5.50 & 6.50 & 66 & 66 & -10.66^{+0.74}_{-1.11} & -29.21^{+1.08}_{-1.89} & -5.05^{+0.76}_{-1.18} & -2.41^{+0.10}_{-0.08} \\
    \hline
  \end{tabular}\\
  \begin{minipage}{13.0cm}
    \textsuperscript{$a$}{Redshift bin not considered in the joint QLF fit due to systematic errors (open circles in Figure~\ref{fig:evoln}).}
  \end{minipage}
\end{table*}
